Type-Safe Modular Parsing

### 2016-12-14 paper/sections/Overview.tex
Remove the pasted code

\begin{lstlisting}
abstract class Expr
class Var(x: String) extends Expr
class App(e1: Expr, e2: Expr) extends Expr

trait BaseParser {
  lexical.delimiters += ("(", ")")
  val pExpr: PackratParser[Expr] = pVar ||| pApp ||| "(" ~> pExpr <~ ")"
  val pVar: PackratParser[Expr] = ident ^^ { x => new Var(x) }
  val pApp: PackratParser[Expr] =
    pExpr ~ pExpr ^^ { case e1 ~ e2 => new App(e1, e2) }
}
\end{lstlisting}

@@

\begin{lstlisting}
class Lam(x: String, e: Expr) extends Expr
\end{lstlisting}

@@

\begin{lstlisting}
trait ExtParser extends BaseParser {
  lexical.delimiters += ("\\", ".")
  val pExtExpr: PackratParser[Expr] =
    pVar ||| pApp ||| pLam ||| "(" ~> pExtExpr <~ ")"
  val pLam: PackratParser[Expr] =
    "\\" ~> ident ~ ("." ~> pExtExpr) ^^ { case x ~ e => new Lam(x, e) }
}
\end{lstlisting}

@@

\begin{lstlisting}
type Open[T] = (=> T) => T

// Expr, Var and App are the same as previous
trait BaseParser {
  lexical.delimiters += ("(", ")")
  val pVar: Open[PackratParser[Expr]] =
    self => ident ^^ { x => new Var(x) }
  val pApp: Open[PackratParser[Expr]] =
    self => self ~ self ^^ { case e1 ~ e2 => new App(e1, e2) }
  val pExpr: Open[PackratParser[Expr]] =
    self => pVar(self) ||| pApp(self) ||| "(" ~> self <~ ")"
}
\end{lstlisting}

@@

\begin{lstlisting}
def fix[T](f: Open[T]): T = { lazy val a: T = f(a); a }

def parse[E](p: Open[PackratParser[E]])(inp: String): E = {
  val t = phrase(fix(p))(new lexical.Scanner(inp))
  if (t.successful) t.get else scala.sys.error(t.toString)
}

println(parse(new BaseParser {}.pExpr)("x y"))
\end{lstlisting}

\bruno{You are copying and pasting code into the paper. Don't do this:
code will change alot (various edits), and it is all too easy to get
inconsistent code snippets. Instead use the small Ruby tool that we
have in the paper directory to import source code directly from the
code repository. This will ensure the consistency of the code
throughout the paper writing. Please ask Haoyuan about the tool; he
knows how to use it!}

@@

\begin{lstlisting}
trait ExtParser extends BaseParser {
  lexical.delimiters += ("\\", ".")
  val pLam: Open[PackratParser[Expr]] =
    self => "\\" ~> ident ~ ("." ~> self) ^^ { case x ~ b => new Lam(x, b) }
  val pExtExpr: Open[PackratParser[Expr]] =
    self => pLam(self) ||| pExpr(self)
}
\end{lstlisting}

@@

\begin{lstlisting}
println(parse(new ExtParser {}.pExtExpr)("(\\x.x) (\\y.y)"))
\end{lstlisting}

>>>>

\lstinputlisting[linerange=8-18]{../Scala/Parser/src/PaperCode/Overview/Overview.scala}% APPLY:linerange=OVERVIEW_SIMPLE_EXPR

@@

\lstinputlisting[linerange=22-22]{../Scala/Parser/src/PaperCode/Overview/Overview.scala}% APPLY:linerange=OVERVIEW_SIMPLE_LAM

@@

\lstinputlisting[linerange=26-32]{../Scala/Parser/src/PaperCode/Overview/Overview.scala}% APPLY:linerange=OVERVIEW_SIMPLE_EXT

@@

\lstinputlisting[linerange=53-63]{../Scala/Parser/src/PaperCode/Overview/Overview.scala}% APPLY:linerange=OVERVIEW_OPEN_BASE

@@

\lstinputlisting[linerange=68-75]{../Scala/Parser/src/PaperCode/Overview/Overview.scala}% APPLY:linerange=OVERVIEW_OPEN_USE

@@

\lstinputlisting[linerange=80-86]{../Scala/Parser/src/PaperCode/Overview/Overview.scala}% APPLY:linerange=OVERVIEW_OPEN_EXT

@@

\lstinputlisting[linerange=95-95]{../Scala/Parser/src/PaperCode/Overview/Overview.scala}% APPLY:linerange=OVERVIEW_OPEN_EXT_USE
